Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-03-07 paper/main.tex

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4in]{figures/ExampleFigures.png}
    \caption{\textbf{A}: Component-aligned, axis-aligned; \textbf{B}: Not component-aligned, axis-aligned;\textbf{C}: Component-aligned, not axis-aligned;\textbf{D}: Not component-aligned, not axis-aligned.\label{fig:examplefigures}}
\end{figure}

@@

@@

\subsection{Sparse class boundaries}

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim1_ev.png}
    \caption{Caption}
    \label{fig:sim1_ev}
\end{figure}

% \begin{figure*}[t!]
%     \centering
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.3in]{figures/simpleboundary.png}
%         \caption{The distribution of the two classes in the first two components. All other components are identically distributed between the two classes.\label{fig:simpleboundary}}
%     \end{subfigure}%

%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.3in]{figures/simpleeigs.png}
%         \caption{The sequence of average projection eigenvalues show a clear distinction for the very first basis vector.}
%     \end{subfigure}
%     ~ 
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.3in]{figures/simplecomponents.png}
%         \caption{Investigating the basis vector corresponding to the distinct eigenvalue shows a strong selection for the first component.}
%     \end{subfigure}
% \caption{}
% \end{figure*}

\subsection{Rotated sparse normal}

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim2_ev.png}
    \caption{Caption}
    \label{fig:sim2_ev}
\end{figure}

% \begin{figure*}[t!]
%     \centering
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexboundary.png}
%         \caption{}
%     \end{subfigure}%
%     ~
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexeigs.png}
%         \caption{}
%     \end{subfigure}

%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexfirst.png}
%         \caption{}
%     \end{subfigure}
%     ~
%     \begin{subfigure}[t]{0.45\textwidth}
%         \centering
%         \includegraphics[height=2.2in]{figures/complexsecond.png}
%         \caption{}
%     \end{subfigure}
% \caption{}
% \end{figure*}

\subsection{Independent features}

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim3_ev.png}[]
    \caption{Caption}
    \label{fig:sim3_ev}
\end{figure}

\subsection{$t$‐distributed features}

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim4_ev.png}
    \caption{Caption}
    \label{fig:sim4_ev}
\end{figure}

@@

% \section{Generalised formulation?}
% If we made good progress on the techniques that we've got at the moment, I think there would be scope for looking at a range of generalisations. These can be grouped into alterations of the selection method for choosing random projections, and alterations of the distance measure used to obtain low-dimensional representations. Consider the following (very general) setup, where we have a few objects:
% \begin{itemize}
%     \item A training set $\mathcal{T}_n$.
%     \item A collection of projections $\mathcal{A} := \{ A_b \in \mathbb{R}^{d\times p} : b \in \{ 1,\dots,B\}$ (by projections we mean that for all $b$, $A_bA_b^T = I_d$).
%     \item A base classifier, i.e. a map $C : (\mathcal{T}_n, A) \mapsto C^A_{\mathcal{T}_n}$ where $C^A_{\mathcal{T}_n}$ is a function $C^A_{\mathcal{T}_n}: \mathcal{X} \rightarrow \mathcal{Y}$.
%     \item A selection procedure, by which we mean a map $s : (\mathcal{T}_n, \mathcal{A}, b, C) \mapsto s_b$ where $s_b:\mathcal{X}^2 \rightarrow \{0,1\}$ is a function detailing which pairs of observations to select that projection for. 
%     \item A positive definite kernel $k: \mathbb{R}^d \times \mathbb{R}^d \rightarrow \mathbb{R}$.
% \end{itemize}

% Now we define a learned distance

% \[K^\mathcal{A}_{\mathcal{T}_n}(x,x') = \sum_{b: s_b(x,x') = 1} k(A_bx, A_bx').\]

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4in]{../results/figures/ExampleFigures.png}
    \caption{\textbf{A}: Component-aligned, axis-aligned; \textbf{B}: Not component-aligned, axis-aligned;\textbf{C}: Component-aligned, not axis-aligned;\textbf{D}: Not component-aligned, not axis-aligned.\label{fig:examplefigures}}
\end{figure}

@@

- Sliced Inverse Regression(!) -\\

@@

\subsection{Sparse class boundaries}
Here we let 
\[X \ | \ \{Y = 0\} \sim \frac{1}{2}N_p(\mu_0, \Sigma) + \frac{1}{2}N_p(-\mu_0, \Sigma) \]
\[X \ | \ \{ Y = 1\} \sim \frac{1}{2}N_p(\mu_1, \Sigma) + \frac{1}{2}N_p(-\mu_1, \Sigma) \]

\subsection{Rotated sparse normal}
Here,

\[X \ | \ \{Y=0\} \sim N_p(\Omega_p\mu_0, \Omega_p \Sigma_0 \Omega_p^T)  \] 
\[X \ | \ \{Y = 1\} \sim N_p(\Omega_p\mu_1, \Omega_p\Sigma_1\Omega_p^T)  \]

\begin{figure}
    \centering
    \includegraphics[width=6in]{../results/figures/sim_evs.png}
    \caption{Caption}
    \label{fig:sim1_ev}
\end{figure}

@@
